---
title: "PS07-Animation in R"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Using Gapminder for animation 


This article describes how to create animation in R using the gganimate R 
package.

According to the article,*gganimate: How to Create Plots with Beautiful
  Animation in R*,
"Gganimate is an extension of the ggplot2 package for creating animated ggplots.
It provides a range of new functionality that can be added to the plot object 
in order to customize how it should change with time."

These are the following key features of gganimate stated from the article:

1.Transitions: you want your data to change

2.Views: you want your viewpoint to change

3.Shadows: you want the animation to have memory

## The Packages needed 


```{r cars}
library(ggplot2)
library(gganimate)
theme_set(theme_bw())
library(gapminder)
```


## Static Plot 

Note: the following code is also taken from the article
```{r pressure}
p <- ggplot(
  gapminder, 
  aes(x = gdpPercap, y=lifeExp, size = pop, colour = country)
  ) +
  geom_point(show.legend = FALSE, alpha = 0.7) +
  scale_color_viridis_d() +
  scale_size(range = c(2, 12)) +
  scale_x_log10() +
  labs(x = "GDP per capita", y = "Life expectancy")
p

```

## The Basics 

1.  `transition_time()`. The transition length between the states will be set to
correspond to the actual time difference between them.

2. Label variables: `frame_time`. Gives 
the time that the current frame corresponds to



## Applying the Basics for transitions through years


```{r}
p + facet_wrap(~continent) +
  transition_time(year) +
  labs(title = "Year: {frame_time}")
```



##  Reference
^[Alboukadel, Transition_reveal, 
Draga, Tiago, W, C., Danhrogers, Thaung, K., Sylvan, 
Kassambara, Kebede, M., Ankit, G, P., Saldaña, S., Mark, 
Lockwood, R. N., Petchulia, Z., Samuel, D. D. K., Artjuch, D., Mehmet, 
&amp; Anthony. (2019, December 25). Gganimate: How to create plots with 
beautiful animation in R. Datanovia. Retrieved December 3, 2021, from https://www.datanovia.com/en/blog/gganimate-how-to-create-plots-with-
beautiful-animation-in-r/. ]
