---
title: "PS07-Gapminder"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Gapminder

This is an R Markdown format used for publishing markdown documents to GitHub.
When you click the **Knit** button all R code chunks are run and a markdown 
file (.md) suitable for publishing to GitHub is generated.


This article describes how to create animation in R using the gganimate R 
package.

According to the article,*gganimate: How to Create Plots with Beautiful 
Animation in R*,
"Gganimate is an extension of the ggplot2 package for creating animated ggplots.
It provides a range of new functionality that can be added to the plot object 
in order to customize how it should change with time."

"Key features of gganimate:

1.transitions: you want your data to change
2.views: you want your viewpoint to change
3. shadows: you want the animation to have memory" - from article

## Including Code

You can include R code in the document as follows:

```{r cars}
library(ggplot2)
library(gganimate)
theme_set(theme_bw())
library(gapminder)
head(gapminder)
```
Code is taken from here: ^[Alboukadel, Transition_reveal, 
Draga, Tiago, W, C., Danhrogers, Thaung, K., Sylvan, 
Kassambara, Kebede, M., Ankit, G, P., Saldaña, S., Mark, 
Lockwood, R. N., Petchulia, Z., Samuel, D. D. K., Artjuch, D., Mehmet, 
&amp; Anthony. (2019, December 25). Gganimate: How to create plots with 
beautiful animation in R. Datanovia. Retrieved December 3, 2021, from https://www.datanovia.com/en/blog/gganimate-how-to-create-plots-with-
beautiful-animation-in-r/. ] 
## Including Plots

You can also embed plots, for example:
Note: the following code is also taken from the article
```{r pressure, echo=FALSE}
p <- ggplot(
  gapminder, 
  aes(x = gdpPercap, y=lifeExp, size = pop, colour = country)
  ) +
  geom_point(show.legend = FALSE, alpha = 0.7) +
  scale_color_viridis_d() +
  scale_size(range = c(2, 12)) +
  scale_x_log10() +
  labs(x = "GDP per capita", y = "Life expectancy")
p


 
p + facet_wrap(~continent) +
  transition_time(year) +
  labs(title = "Year: {frame_time}")

```

Note that the `echo = FALSE` parameter was added to the code chunk to 
prevent printing of the R code that generated the plot.
